---
title: "Simple document"
author: "null"
date: "null"
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: hide
---

```{r}
library(tidyverse)
```


I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3 

Let's write a new code chunk (option, command, I)

This code chunk imports the 'tidyverse', creates a data frame, and makes a histogram


```{r, message=FALSE}

set.seed(1234) 

plot_df = 
  tibble(
    x = rnorm(1000, sd = .5),
    y = 1 + 2 * x + rnorm(1000)
  )

ggplot(plot_df, aes(x = x)) + geom_histogram() 

ggplot(plot_df, aes(x = x, y = y)) + geom_point() 
```

# Learning Assessment 1

Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?


```{r}
learningassessment_df = 
  tibble(
    sample = rnorm(500, mean = 1), 
    gr_than_0 = sample > 0, 
    abs_val = abs(sample)
  )

ggplot(learningassessment_df, aes(x = abs_val)) + geom_histogram() 
```

